The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-20 science_ms.tex
Changed abstract to be more Science-like.

\begin{sciabstract}
  Population III stars first form in dark matter halos with masses
  around $10^6~\Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that follows the
  transition from Population III to II star formation.  We model
  stellar radiative feedback with adaptive ray tracing.  A top-heavy
  initial mass function for the Population III stars is considered,
  resulting in a plausible distribution of pair-instability supernovae
  and associated metal enrichment.  We find that the gas fraction
  recovers from 5 percent to nearly the cosmic fraction in halos with
  merger histories rich in halos above $10^7~\Ms$.  A single
  pair-instability supernova is sufficient to enrich the host halo to
  a metallicity floor of $10^{-3}~Z_\odot$ and to transition to
  Population II star formation.  Neighboring halos are enriched to
  metallicities 10--100 times lower as the enriching blastwaves mainly
  bypass them.  Stellar metallicities trace gas metallicities within
  0.2 dex.  We find that stellar metallicities do not necessarily
  trace stellar ages, as mergers of halos with established stellar
  populations can create superpositions of $t-Z$ evolutionary tracks.
  A bimodal metallicity distribution is created after a starburst
  occurs when the halo can cool efficiently through atomic line
  cooling.
\end{sciabstract}

>>>>

\begin{sciabstract}
  Supernova explosions from the first stars in the universe, which are
  predicted to be very massive, chemically enriched the intergalactic
  medium, originally a primordial mix of hydrogen and helium.  A
  fraction of these metals propagate into star-forming regions,
  providing more efficient cooling mechanisms and, in turn, increasing
  gaseous fragmentation in the first stellar clusters.  Here, we
  report on the birth of two high-redshift dwarf galaxies in a
  cosmological radiation hydrodynamics simulation.  We find that only
  one supernova is sufficient to enrich the nearby star-forming gas
  with a floor of 1/1,000 of the solar metallicity ratio, preventing
  any further metal-free star formation within 10 kpc of the past
  explosion.  We follow the entire star formation history of these
  galaxies, providing robust models to interpret the stellar
  populations of nearby dwarf galaxies and future observations of
  high-redshift dwarf galaxies.
\end{sciabstract}
